---
title: "Week 3 Assigment"
author: "José Manuel Peñas"
date: "August 25, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2);library(plotly)
```

## Overview

This presentation is going to use the same data used on week 2 assigment:
- the dataset with the French municipalities seen on [r-bloggers](https://www.r-bloggers.com/french-dataset-population-and-gps-coordinates/).
This document will show an interactive scatter plot that will compare the growth population between the period **1975-2010** with the population recorded at the begining of the study on **1975**.


## Getting & Cleaning the data
Now, the following steps are going to be taken in order to get and clean the data to show in the plot.

- Download the csv file from the original web
```{r getting, echo=FALSE}
if (!file.exists("./data/popfr19752010.csv")) {
      download.file(
      "http://freakonometrics.free.fr/popfr19752010.csv","./data/popfr19752010.csv"
      )
      
}
popfr=read.csv("./data/popfr19752010.csv",header=TRUE, stringsAsFactors = F)
```
- Keep only commune names and the population at 1975 and 2010.
```{r cleaning_columns, echo=FALSE}
popfr <- subset(popfr[,c(5,8,43)],pop_2010 > 10000)
```

- Create a new column with percentage growth between 1975 and 2010.
```{r growth, echo=FALSE}
popfr$growth <- (popfr$pop_2010 - popfr$pop_1975)/popfr$pop_1975*100
popfr <- subset(popfr, growth < 100)
head(popfr)
```


## Plot with GGPlotly

```{r pressure, echo=FALSE, message=FALSE}
g <- ggplot(data=popfr,aes(x=log10(pop_1975), y=growth))+ geom_point(data=popfr, alpha=.5) + geom_smooth()
gg <- ggplotly(g)
gg
```

## Plot with Plotly

```{r plotly, echo=FALSE, message=FALSE}
plot_ly(data=popfr,x=log10(popfr$pop_1975),y=popfr$growth, mode="markers")
```
